\documentclass{resume}

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}


\name{Tran Duy Tuan}

\def\nameskip{\bigskip}
\def\sectionskip{\medskip}

\begin{document}

  %%% Personal details
  %%% ------------------------------------------------------------
  \PersonalEntry{Phone}{(+84) 37 985 3282}
  \PersonalEntry{Mail}{\href{mailto:trantuan1892@gmail.com}{trantuan1892@gmail.com}}
  \PersonalEntry{LinkedIn}{\url{https://linkedin.com/in/tuan-tran-3115b9171/}}
  \PersonalEntry{GitHub}{\url{https://github.com/HeligPfleigh}}
  \PersonalEntry{SO}{\url{https://stackoverflow.com/users/5832644/tuan-tran}}
  \PersonalEntry{Birth}{December 18, 1992}
  \PersonalEntry{Address}{Hanoi}

  %%% Overview
  %%% ------------------------------------------------------------
  I'm an experienced developer interested in building usable, useful, well-constructed websites and \\applications. 
  Interested in continuation of learning and cooperation with excellent people. 

  %%% Skills
  %%% ------------------------------------------------------------
  \begin{rSection}{Technical skill}
    \begin{tabular}{ @{} @{} l }
      Strong knowledge at HTML \& CSS. \\
      Language: Javascript, Typescript, Java, C++, Python. \\
      Experience with React, Redux, Mobx, MaterialUI and Bootstrap \\
      Familiarity with Docker and containerized deployment \\
      Backend: Node, Express, Koa, GraphQL. \\
      Cross-platform: React Native, Electron \\
      Database: MongoDB, PostgreSQL \\
      Familiarity with mobile application build/roll out process, and native build tool \\
      Tools: Git, Vim, VSCode
    \end{tabular}
  \end{rSection}
  
  %%% Exp
  %%% ------------------------------------------------------------
  \begin{rSection}{Experience}
    \begin{rSubsection}{MTT Software Company}{November 2017 - Present}{Fullstack JavaScript Developer}{}
    \item Develop dynamic and responsive web/mobile app with clean interface and simple, instuitive interaction
    \item Develop project concepts and maintain optimal workflow.
    \item Participate in database design and api backend tasks.
    \item Carry out quality assurance unit tests to discover errors and optimize usability.
    \\\\
    \href{https://mttjsc.com/}{\emph{MTT Website}}: An affiliate website for MTT.
    \\\emph{Nailshop Ecosystem} (\href{https://play.google.com/store/apps/developer?id=MTT+Software+Company+LTD/}{\emph{Android}}/\href{https://apps.apple.com/us/developer/mttjsc/id1250334932}{\emph{IOS}}): 
    An ecosystem to provide service for nailshop owner manager their
    staff, schedule their working timeline, get monthly statistic report and connect customer with shops.
    \\\href{http://app.faktoora.com}{\emph{Faktoora}}: E-billing system.
    \\\emph{Post Luxemburd}: A log analysis system base on Splunk platform which provide intuitive view for network attack.
    \\\emph{I Feel Good} (\href{https://play.google.com/store/apps/details?id=com.ifg_mobile}{\emph{Android}}/\href{}{\emph{IOS}}): 
    An utility application which highlights in a glance all the factors that have an impact on your physical and mental health.
    \\\href{https://app.scnt.me/}{\emph{Scentronix}}: A PWA web app which help people select their favorite perfume ingredients to make their own one.
    \\\href{https://www.madlogic.nl/magic/}{\emph{Madlogic}}: A communication application for organizations that want to reach and connect all employees quickly.
    \end{rSubsection}
  
    \begin{rSubsection}{SVMC}{April 2016 - November 2017}{C++ Developer}{}
    \item Using MFC, opencv to make utility application on window
    \item Developed and maintained PST tool which help check phone infomation for manufacturing samsung models
    \item Participated in researching about image processing to develop a utility tool to track and recognize infection in each phone
    \item Developed, maintained and documentation for SRA/SUA/Smartswitch application
    \end{rSubsection}
  
  \end{rSection}

  %%% Others
  %%% ------------------------------------------------------------
  \begin{rSection}{Education}
    {\bf Hanoi University of Science and Technology} \\ 
    { B.S. in Information Technology (CTES program) } \\
  \end{rSection}

  \begin{rSection}{Languages}
    {\bf English} \\ 
    { TOEIC Certificate scored 805  } \hfill {\em August 2017 - August 2019} \\
  \end{rSection}

\end{document}
